Test susieI using chr17 to 22

### 2020-09-01 analysis/simulation-multi-ukbchr17to22-gtex.adipose_susieprior.Rmd
increase gene pve

# PIP calibration: filter regions

```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/20200721-1-fixprior_rpip0.5/"
```

We run 100 simulations and run susie using different priors and `L= 1`. We only apply susie for regions with mr.ash2 regional PIP > 0.5.

@@

# PIP calibration: use all regions

```{r output dir all}
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/"
```

We run 100 simulations and run susie using different priors and `L= 1`. We only apply susie for all regions.

@@

* The true parameters we used to simulate data: 
```{r  true par all}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_1.txt"), header = T)
t(par[,2, drop = F])
```

@@

```{r cali 0 all, fig.height=6, fig.width=6}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior1.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))

@@

* The prior used is: 
```{r  par1 all}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1 all, fig.height=6, fig.width=14}
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

* The prior used is: 
```{r  par2 all}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
```

```{r cali 2 all, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior2.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))

@@

* The prior used is: 
```{r  par3 all}
par <- read.table(paste0(susiedir, "20200721-1-fixedprior_3.txt"), header = T)
t(par[c(1,3),1, drop = F])
```

* susie results: 
```{r cali 3 all, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-1-*.fixedprior3.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))

>>>>

# Setting 1

```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/"
```

We run 50 simulations and run susie using different priors and `L= 1`. We apply susie for all regions.

@@

# Setting 2

We run 100 simulations and run susie using different priors and `L= 1`. We apply susie for all regions.

@@

* The true parameters we used to simulate data: 
```{r  true par all}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_1.txt"), header = T)
t(par[,2, drop = F])
```

@@

```{r cali 0 all, fig.height=6, fig.width=6}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior1.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))

@@

* The prior used is: 
```{r  par1 all}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_1.txt"), header = T)
t(par[c(1,3),1, drop = F])
```
* susie results: 
```{r cali 1 all, fig.height=6, fig.width=14}
par(mfrow=c(1,2))
cp_plot(res$pip, res$ifcausal, main = "SUSIE.weighted PIP")
cp_plot(res$pip.w0, res$ifcausal, main = "SUSIE.weighted-w-null PIP")
```

@@

* The prior used is: 
```{r  par2 all}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_2.txt"), header = T)
t(par[c(1,3),1, drop = F])
```

```{r cali 2 all, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior2.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))

@@

* The prior used is: 
```{r  par3 all}
par <- read.table(paste0(susiedir, "20200721-3-fixedprior_3.txt"), header = T)
t(par[c(1,3),1, drop = F])
```

* susie results: 
```{r cali 3 all, fig.height=6, fig.width=14}
pipfs <- Sys.glob(paste0(susiedir,"20200721-3-*.fixedprior3.L1.susieres.expr.txt"))
res <- do.call(rbind, lapply(pipfs, read.table, header = T))

### 2020-09-01 analysis/simulation-susieI-ukbchr17to22-gtex.adipose.Rmd
increase gene pve

* Susie run parameters: `L=1`, `null_weight = 0`, didn't update `null_weight` in iterations.

@@

  pars <- cbind(param[seq(1,nrow(param), 2), 1], param[seq(2,nrow(param), 2), 1], param[seq(1,nrow(param), 2), 3], param[seq(2,nrow(param), 2), 3])
  colnames(pars) <- paste(rep(c("pi1.gene_", "pi1.SNP_"), each = 2), c("truth", "mr.ash2"), sep = "")

@@

  df %>% 
  kable("html", escape = F) %>%
  kable_styling("striped", full_width = F) %>%
  scroll_box(width = "100%")

}

@@

* Susie run parameters: `L=1`. Initiate with `null_weight = 0` and update `null_weight` based on last iteration results.

@@

```{r param2}
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config1.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config1.susieI.txt")

@@

* Susie run parameters: `L=2`. Initiate with `null_weight = 0` and update `null_weight` based on last iteration results.

@@

* Susie run parameters: `L=1`. Did not update `null_weight` in each iteration.

@@

>>>>

* Susie run parameters: `L=1`, `null_weight = 0`, didn't update `null_weight` in iterations. We initialize with prior for genes and SNPs as uniform.

@@

  pars <- cbind(param[seq(1,nrow(param), 2), 2], param[seq(1,nrow(param), 2), 4], param[seq(1,nrow(param), 2), 1], param[seq(2,nrow(param), 2), 1], param[seq(1,nrow(param), 2), 3], param[seq(2,nrow(param), 2), 3])
  colnames(pars) <- c("PVE.gene_truth", "PVE.SNP_truth", paste(rep(c("pi1.gene_", "pi1.SNP_"), each = 2), c("truth", "mr.ash2"), sep = ""))

@@

  df %>% 
  kable("html", escape = F) %>%
  kable_styling("striped", full_width = F) %>%
   row_spec(c(1:5, 11:15), background = "#FEF3B9") %>%
  scroll_box(width = "100%", height = "600px", fixed_thead = T)
}

@@

* Susie run parameters: `L=1`. initialize with `null_weight = 0` and update `null_weight` based on last iteration results. We initialize with prior for genes and SNPs as uniform.

@@

```{r param2}
tags <- paste(rep(1:4, each = 5), 1:5, sep = "-")
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config1.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config1.susieI.txt")

@@

* Susie run parameters: `L=2`. initialize with `null_weight = 0` and update `null_weight` based on last iteration results. We initialize with prior for genes and SNPs as uniform.

@@

* Susie run parameters: `L=1`. Did not update `null_weight` in each iteration. We initialize with prior for genes and SNPs as uniform.

@@

# susieI genes - setting 5

* Susie run parameters: `L=2`. Update `null_weight` in each iteration. We initialize prior for gene as `0.05` and prior for SNPs as `2.5E-3`, we initialize `null_weight` as 0.

Prior change for each iteration:
```{r iter5}
load(paste0(outputdir, tag, ".config4.susieIres.Rd"))
df <- cbind(prior.gene_rec, prior.SNP_rec)
rownames(df) <- paste("Iteration", 1:Niter)
colnames(df) <- c("Prior.gene", "Prior.SNP")
df
```

```{r param5}
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config4.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config4.susieI.txt")
